\documentclass[a4paper, serif, 11pt]{moderncv}

%% moderncv
% style and color
\moderncvstyle{banking}
\moderncvcolor{black}

%% page layout/margins
\usepackage[top=2.5cm, bottom=2.5cm, left=1.5cm, right=1.5cm]{geometry}

%% Babel config for English language
\usepackage[english]{babel}

%% fontspec
\usepackage{fontspec}

\IfFontExistsTF{Linux Libertine}{
  \setmainfont[Ligatures={TeX, Common}, Numbers=OldStyle]{Linux Libertine}
}{}
\IfFontExistsTF{Linux Libertine O}{
  \setmainfont[Ligatures={TeX, Common}, Numbers=OldStyle]{Linux Libertine O}
}{}

%% CTeX
% CJK support, used to show CJK characters in the resume
%
% - fontset=none: disable builtin fontset but instead set the CJK font manually
% - heading=false: disable ctex heading
% - punct=kaiming: use kaiming punctuations styles for CJK
% - scheme=plain: use plain scheme, do not override \normalsize font size
% - space=auto: space settings for CJK characters
%
% ref:
% - http://ctan.mirrorcatalogs.com/language/chinese/ctex/ctex.pdf
\usepackage[UTF8, heading=false, punct=kaiming, scheme=plain, space=auto]{ctex}

\IfFontExistsTF{Noto Serif CJK SC}{
  \setCJKmainfont{Noto Serif CJK SC}
}{}
\IfFontExistsTF{Noto Sans CJK SC}{
  \setCJKsansfont{Noto Sans CJK SC}
}{}

%% line spacing
\usepackage{setspace}
\setstretch{1.125}

%% URL styling - use normal text instead of monospace
\urlstyle{same}

% Auto-underline all links
% Defer until \begin{document} so hyperref is already loaded
\AtBeginDocument{%
  \let\oldhref\href
  \renewcommand{\href}[2]{\oldhref{#1}{\underline{#2}}}%
}

%% Patch \httplink and \httpslink to handle full URLs
% The original moderncv macros always prepend http:// or https:// to URLs.
% This causes issues when the URL already has a protocol (e.g., https://example.com)
% resulting in malformed URLs like https://https://example.com.
% This patch checks if the URL already contains "://" and uses it directly if so.
% Note: We use \str_set:Nx (x-expansion) to expand macros like \@homepage first.
\ExplSyntaxOn
\str_new:N \g_yamlresume_url_str

\RenewDocumentCommand{\httpslink}{O{}m}{
  \str_set:Nx \g_yamlresume_url_str {#2}
  \str_if_in:NnTF \g_yamlresume_url_str {://}
    { \url{#2} }
    { \url{https://#2} }
}

\RenewDocumentCommand{\httplink}{O{}m}{
  \str_set:Nx \g_yamlresume_url_str {#2}
  \str_if_in:NnTF \g_yamlresume_url_str {://}
    { \url{#2} }
    { \url{http://#2} }
}
\ExplSyntaxOff

\name{Volodymyr Protsaylo}{}
\title{Software Engineer (Java)}
\email{wolodya.java@manyme.com}

\address{Lviv, Ukraine}{}{}

\extrainfo{{\small \faLinkedin}\ \href{https://www.linkedin.com/in/protsaylo/}{@protsaylo}}

\begin{document}

\maketitle

\section{Basics}

\cvline{}{\begin{itemize}
\item Computer Science graduate with a deep foundation in data structures, algorithms, and robust software design.
\item Java developer with over two decades of IT experience, including 10+ years specializing in Java backend development.
\item Extensive experience designing AML/KYC risk-scoring and authentication platforms for tier-one Nordic banks.
\item Broad domain background spanning fintech, banking, healthcare, media, and oil \& gas across Europe, the Middle East, and the US.
\item Deep technical expertise in Spring Boot, event-driven architectures (Kafka), and secure enterprise authentication (OIDC/SAML).
\item Proven track record of delivering production-critical systems under tight compliance and high-pressure environments.
\end{itemize}}
\section{Education}

\cventry{1994–1999}
        {Master, Computer Sciences, Score: 5.0}
        {Lviv Polytechnic National University}
        {\url{https://lpnu.ua/en}}
        {}
        {Department of Information Technology Design}
\section{Work}

\cventry{Feb 2024–Present}
        {Senior Software Engineer}
        {Tieto}
        {\url{https://www.tieto.com/en/}}
        {}
        {\textbf{AML/KYC Customer Risk Rating (CRR) Platform (Jan 2026 – Present | Team: 10)}
%
\begin{itemize}
\item Engineered a core CRR engine supporting Anti-Money Laundering (AML) and Know Your Customer (KYC) compliance, automating risk scoring for customer onboarding and periodic reviews.
\item Investigated and resolved a critical database connection leak in the CRR API by optimizing HikariCP connection pooling handling.
\item Enhanced system resilience by refactoring graceful shutdown mechanisms, timeout configurations, and error handling across the CRR API.
\item Extended industry code processing logic to seamlessly handle multiple industry codes per customer during live risk evaluations.
\item Fixed core AML status fallback logic, ensuring reliable synchronous evaluations divert to KYC Core when the primary AML database is unavailable.
\item Implemented comprehensive audit logging (ILO) for CRR actions to satisfy strict regulatory traceability requirements.
\end{itemize}
\textbf{Secure Common Services (SCS) Authentication Platform (Feb 2024 – Jan 2026 | Team: 12)}
%
\begin{itemize}
\item Developed and maintained a high-availability identity and authentication platform integrating BankID, ID-Porten, Buypass, and biometrics for retail banking customers via a unified Identity Provider (IDP) backend.
\item Integrated new authentication flows, including SA-MOBILE-BIOMETRIC-ID and the Simplified BankID flow, across client and IDP services.
\item Resolved complex integration bugs, including an OIDC return flow defect for the PURE-NO-BANKID method and a SAML client verification lookup issue.
\item Diagnosed and fixed low-level Hardware Security Module (HSM) cryptographic exceptions affecting digital signing operations.
\item Designed and implemented secure audit logging (ILO) for administrative and approval workflows, alongside streaming real-time authentication stats, billing, and fraud logs via Kafka.
\end{itemize}}

\cventry{May 2023–Feb 2024}
        {Software Engineer}
        {Infopulse}
        {\url{https://en.wikipedia.org/wiki/Infopulse\_Ukraine}}
        {}
        {\begin{itemize}
\item \textbf{Automotive Retail Banking Solution providing financing and loans for major European car manufacturers (Team: 15).}
\item Analyzed and extended an enterprise OEM data loader solution, consolidating high-volume info from fragmented sources into a single database.
\item Migrated the Vehicle Type Service (VTS) module to a new platform, introducing high-performance caching for commercial vehicle data.
\item Standardized the core VIS API and designed a matching service for OEM data snapshots.
\item Designed an application gateway mapping replacement to ensure seamless integration with a newly introduced core service.
\end{itemize}}

\cventry{Jan 2023–May 2023}
        {Software Engineer}
        {KindGeek}
        {\url{https://www.kindgeek.com/}}
        {}
        {\begin{itemize}
\item ** Digital Retail Banking Platform for the Middle East market (Team: 30).**
\item Extended and integrated core banking engine modules to match local compliance regulations.
\item Mapped and implemented strict Anti-Money Laundering (AML) and Anti-Fraud business logic requirements.
\end{itemize}}

\cventry{Feb 2021–Jan 2023}
        {Software Engineer}
        {ELEKS}
        {\url{https://eleks.com/}}
        {}
        {\textbf{Sport \& Fitness Enterprise Solution (Jan 2022 – Jan 2023 | Team: 20)}
%
\begin{itemize}
\item Refactored and optimized core algorithms to improve platform performance and maintainability for a massive family-oriented fitness group business.
\end{itemize}
\textbf{Retail POS Solution (Apr 2021 – Jan 2022 | Team: 22)}
%
\begin{itemize}
\item Developed a localized retail web app and admin console to configure POS terminals, manage users, and store transaction data.
\item Engineered robust offline-mode functionality for network disruptions and integrated barcode label printing hardware.
\end{itemize}
\textbf{Task Management \& Communication System (Feb 2021 – Apr 2021 | Team: 14)}
%
\begin{itemize}
\item Implemented REST endpoints and database migration scripts using PostgreSQL.
\item Integrated Amazon SES for transactional mailings and Amazon S3 for attachment storage.
\item Produced core technical documentation and open-source library compliance guidelines.
\end{itemize}}

\cventry{Jan 2014–Feb 2021}
        {Software Engineer}
        {Edvantis}
        {\url{https://www.edvantis.com/}}
        {}
        {\textbf{Certification \& Data Analytics Systems (Oct 2018 – Feb 2021 | Teams: 4–5)}
%
\begin{itemize}
\item Designed and developed new features for backend data infrastructure and rolled out new digital certification programs for US clients.
\item Designed, developed, and integrated new backend functionality, fixing defects in existing data infrastructure.
\end{itemize}
\textbf{Media Article Classification Tool (Nov 2017 – Oct 2018 | Team: 12)}
%
\begin{itemize}
\item Built microservices backend infrastructure using Docker containers and established continuous integration pipelines using Jenkins.
\end{itemize}
\textbf{SQL \& Application Development (Jan 2014 – Nov 2017 | Teams: 3–4)}
%
\begin{itemize}
\item Developed complex SQL queries and database optimizations for healthcare reporting based on detailed requirement analysis.
\item Planned, built, and tested analytics platform modules across diverse production environments.
\end{itemize}}

\cventry{Sep 2008–Dec 2013}
        {Java Engineer, System Programming Dept. Manager}
        {Altertech}
        {\url{https://www.altertech.com/}}
        {}
        {\begin{itemize}
\item \textbf{Advertisement Marketplace (Team: 5):}
\item Architected custom software solutions and managed bare-metal server virtualization, monitoring, and automated backup infrastructure.
\item Developed complex automation scripts and open-source storage solutions.
\item Built system management tools and applications for high-volume VoIP platforms.
\end{itemize}}
\section{Languages}

\cvline{English}{Full Professional Proficiency}
\cvline{Polish}{Minimum Professional Proficiency}
\cvline{German}{Minimum Professional Proficiency}
\cvline{Ukrainian}{Native or Bilingual Proficiency}
\section{Skills}

\cvline{Technologies}{Expert \hfill \textbf{Keywords}: Java, Scala, Agile, SQL, Spring Boot, Micronaut, Microstream, MVC, Docker, Kafka, Microservices, REST, CI/CD, Maven, Git, Gradle}
\cvline{Unit Testing}{Advanced \hfill \textbf{Keywords}: JUnit, Mockito, DBRider, WireMock}
\cvline{Build Servers}{Advanced \hfill \textbf{Keywords}: Jenkins, TeamCity, GitLab CI}
\cvline{Web Technologies and Frameworks}{Advanced \hfill \textbf{Keywords}: JSP, Spring MVC, XML/XSLT, HTML5, JavaScript, Apache FreeMarker}
\cvline{Data Access and ORM}{Expert \hfill \textbf{Keywords}: JDBC, JPA, Hibernate}
\cvline{Integration}{Advanced \hfill \textbf{Keywords}: Apache ActiveMQ, Web services, MQTT, Kafka}
\cvline{Web Performance Testing}{Intermediate \hfill \textbf{Keywords}: Selenium IDE, Web Performance Load Tester}
\cvline{Application Servers}{Intermediate \hfill \textbf{Keywords}: Apache Tomcat, Resin}
\cvline{Databases}{Advanced \hfill \textbf{Keywords}: Oracle, PostgreSQL, Microsoft SQL Server, MySQL, Redis, MongoDB}
\section{Certificates}

\cventry{Jan 2020}
        {GrepS}
        {Skill Analysis for Professional Java Developers}
        {}
        {}
        {}

\cventry{Jan 2019}
        {LITS}
        {Basics of Web UI Development}
        {}
        {}
        {}

\cventry{Jan 2018}
        {Coursera}
        {Learning How to Learn}
        {}
        {}
        {}

\cventry{Jan 2017}
        {LITS}
        {CS50: Introduction to Computer Science}
        {}
        {}
        {}
\section{Interests}

\cvline{Sports}{Swimming, Bike, Hiking}
\cvline{Technical}{Internet of Things (IoT), Amateur Radio Operation, 3D Printing}
\end{document}